%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
	\cventry
		{Director, Sam's Clbu Computer Vision Group} % Job title
		{Walmart Global Tech} % Organization
		{Dallas, TX} % Location
		{Apr. 2025 - Present} % Date(s)
		{
			\begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Oversee Sam's Club Computer Vision group (150+) to innovate, build and operate AI solutions for in-club retail applications.}
          \vspace{4mm}
          \begin{cvitems}
            \item {IRAS: Manage club insights with autonomous floor scrubbers robots for inventory accuracy, club operation safety, and on-shelf availability.}
            \item {Just Go®: Frictionless Exit Technology with sensor fusion of cameras and RFIDs at Sam’s Club in all 600+ clubs nationwide.}
            \item {ISEE: Whole-store camera system for frictionless shopping and store operation automation.}
          \end{cvitems}
        \item {Spearhead various POC applications for in-club safety, member experience, shrink prevention, and operation efficiency.}
          \vspace{4mm}
          \begin{cvitems}
            \item {Drive map services for inventory locations and club layout for both assoicates and members.}
            \item {Explore digital twin and 3D vision applications for in-store operation optimization.}
            \item {Build on-device and edge computer vision platforms for in-club real-time applications.}
            \item {Leverage Generative AI for transforming team productivity, associate engagement, and member experience.}
          \end{cvitems}
        \item {Grow a leadership team, tech thought leaders and cross-functional teams to deliver end-to-end products with measurable business impact.}
          \vspace{4mm}
          \begin{cvitems}
            \item {Recruit, mentor, and develop engineering managers, data science managers, and individual contributors.}
            \item {Manage a large group of contractors and vendors to deliver high-quality products on time.}
            \item {Coordinate with operation, legal, privacy, and security teams to ensure compliance with regulations and company policies.}
            \item {Foster a culture of innovation, collaboration, and continuous learning within the team.}
          \end{cvitems}
        \item {Collaborate with other parts of the tech teams, product groups, and business units to drive coherent AI strategy and execution.}
			\end{cvitems}
		}

	\cventry
		{Senior Manager II, Sam's Club AI Labs} % Job title
		{} % Organization
		{} % Location
		{Jul. 2023 - Apr. 2025} % Date(s)
		{
			\begin{cvitems} % Description(s) of tasks/responsibilities
				\item {Built and grew cross-functional distributed teams (onshore and offshore) 
				of data scientists, engineers (MLE, DE, SDE), and architects.}
				\item {Drove comprehensive roadmaps across products, including forecast, risk 
				analysis, optimization, and Generative AI.}
				\item {Developed initiatives among leaderships and work with stakeholders to ensure 
				end-to-end product delivery with measurable business impact.}
				\item {Oversaw architectural transformation in MLOps to build reliable and 
				repeatable machine learning systems.}
				% \item {Manage team performance, couch individual contributors / people %
				% leaders, and foster a culture of innovation.}
			\end{cvitems}
		}

	\cventry
		{Senior Manager I, Sam's Data Science and Engineering} % Job title
		{} % Organization
		{} % Location
		{Apr. 2022 - Jul. 2023} % Date(s)
		{
			\begin{cvitems} % Description(s) of tasks/responsibilities
				\item {Led data science and machine learning engineering teams to build a demand 
				forecast platform for retail applications.}
				\item {Built data driven solutions for merchandise/procurement, supply chain 
				optimization, and financial modeling.}
				\item {Managed product roadmaps, team execution, and stakeholders' expectations.}
				\item {Drove platform adoption via cross-team leveraging, inner sourcing, and 
				joint development among different teams.}
			\end{cvitems}
	}

%---------------------------------------------------------
\cventry
{System Engineer, Team Lead} % Job title
{Texas Instruments} % Organization
{Dallas, TX} % Location
{May. 2018 - Apr. 2022} % Date(s)
{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Led a team on HW-SW co-design and machine learning performance optimization 
			on embedded devices.}
			\item {Supported market and app teams on in winning and maintaining customers and had 
			an impact on generating multi-million revenue.}
			\item {Mentored and supervised team members on career development and cross-functional projects.}
			% \item {Supported internal digital design teams (RTL coding) for %
			% specifications of model deployment on embedded systems.}
			\item {Researched and developed algorithm and on-chip solutions on efficient neural 
			networks with compressed, sparse, and quantized models.}
			\item {Benchmarked state-of-art CV, NLP, and ASR models and built a model zoo of 
			modified models optimized for embedded devices.}
			\item {Built a hybrid infrastructure (AWS + On-premise) to facilitate MLOps 
			pipelines for deep learning training on GPUs.}
			% \item {Built and maintained on-premise servers for deep learning training %
			% with yearly hardware upgrades.}
		\end{cvitems}
}


\cventry
{Research Intern} % Job title
{} % Organization
{} % Location
{May. 2018 - July. 2018} % Date(s)
{
		\begin{cvitems} % Description(s) of tasks/responsibilities
				\item {Researched on efficient neural networks for embedded devices.}
				\item {Prototyped novel quantization scheme for sub 8-bit fixed-point arithmetics 
				for deep learning models.}
				% \item {Benchmark convolutional neural network (CNN) performance for %
				% vision tasks on TI hardware.}
		\end{cvitems}
}

%---------------------------------------------------------
	\cventry
		{Research Assistant} % Job title
		{Georgia Institute of Technology} % Organization
		{Atlanta, GA} % Location
		{Sep. 2014 - Aug. 2019} % Date(s)
		{
			\begin{cvitems} % Description(s) of tasks/responsibilities
				\item {Led the research and deployment of machine learning systems on large-scale %
				datasets from data acquisition to web services.}
				\item {Supervised junior Ph.D. and Master students in interdisciplinary research.}
				\item {Developed and support open-source and proprietary research softwares for %
				industry and government sponsors.}
				% \item {Developed and support in-house numerical (FD) simulation tools for %
				% elastic wave propagation in complex medium.}
				% \item {Maintained HPC server and optimized for storage and processing of %
				% large-scale datasets.}
			\end{cvitems}
		}

%---------------------------------------------------------
	\cventry
		{Research Intern} % Job title
		{Houston Research Center, Aramco Service Company} % Organization
		{Houston, TX} % Location
		{Aug. 2015 - Nov. 2015} % Date(s)
		{
			\begin{cvitems} % Description(s) of tasks/responsibilities
				\item {Prepared and organized large-scale seismic datasets from land acquisition %
				for machine learning models.}
				\item {Developed algorithms to process land acquisition data searching for small %
				events in the noisy environment.}
				\item {Designed and evaluated machine learning systems for dimension reduction, %
				image segmentation and object tracking.}
				% \item {Built tools to enhance signal quality and cancel noise using %
				% dictionary learning backed algorithms.}
			\end{cvitems}
		}

%---------------------------------------------------------
	\cventry
		{Research Intern} % Job title
		{Microsoft Research} % Organization
		{Redmond, WA} % Location
		{May. 2014 - Aug. 2014} % Date(s)
		{
			\begin{cvitems} % Description(s) of tasks/responsibilities
				\item {Prototyped a non-linear numerical simulation tool for ultrasonic wave in %
				\textit{C++} with a \textit{MATLAB} interface.}
				\item {Conducted acoustic measurements in anechoic chamber testing phase-array %
				prototype products.}
				\item {Published and presented results in research paper and conferences.}
			\end{cvitems}
		}

%---------------------------------------------------------
	\cventry
		{Research Co-op} % Job title
		{Bose Coporation} % Organization
		{Framingham, MA} % Location
		{Jan. 2012 - Dec. 2012} % Date(s)
		{
			\begin{cvitems} % Description(s) of tasks/responsibilities
				% \item {Worked with marketing team in identifying customer's requirements %
				% and make product definition.}
				\item {Worked with transducer team to designed and simulated transducer array %
				using their newly developed waveguide and subwoofer.}
				\item {Built prototype speaker system on wood frame and developed noise %
				reduction circuit for power amplifier.}
				% \item {Measured and evaluated acoustic system in both anechoic chamber and %
				% living room setup (both objective and subject evaluations).}
				\item {Worked in the early stage prototyping of accoustic and electronic system %
				for Bose Solo series with different form factors.}
				% \item {Design went into development and eventually became a mass market product.}
				% \item {Developed and maintained \textit{MATLAB} and \textit{Perl} script to %
				% automate accostic testing procedure.}
				% \item {Assisted adaptive microphone array design for conference setup.}
			\end{cvitems}
		}

%---------------------------------------------------------
	\cventry
		{Automation Intern} % Job title
		{Robert Bosch GmbH} % Organization
		{Suzhou, China} % Location
		{May. 2011 - Aug. 2011} % Date(s)
		{
			\begin{cvitems} % Description(s) of tasks/responsibilities
				\item {Developed and optimized PLC programs to enhance automation of %
				manufacturing processes}.
				\item {Maintained and improved a database system fro manufacturing data %
				logging, enabling effective root cause analysis and process optimization.}
				\item {Created unit test and quality control for software development, %
				ensuring reliable and error-free automation system in production.}
			\end{cvitems}
		}

%---------------------------------------------------------
\end{cventries}
